Accuracy and precision of zero-heat-flux temperature monitoring

### 2019-12-06 manuscript/manuscript.Rmd
extra formatting as per anesthesiology

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
subtitle: A systematic review and meta-analysis
description: "A systematic review and meta-analysis"
author:
- name: Aaron Conway
  affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca
  url: https://www.aaronconway.info
- name: Megan Bittner
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Dan Phan
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Navpreet Kamboj
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: navpreet.kamboj@mail.utoronto.ca
- name: Kristina Chang
  affiliation: Toronto General Hospital, UHN
- name: Elizabeth Tipton
  affiliation: Department of Statistics, Northwestern University
- name: Matteo Parotto
  affiliation: Toronto General Hospital, UHN
date: "`r Sys.Date()`"
repository_url: https://github.com/awconway/zhf-review
twitter:
  creator: "@aw_conway"
output: distill::distill_article
bibliography: Extras/bibliography.bib
csl: Extras/anesthesiology.csl
# author:
#   - Aaron Conway PhD:
#       email: aaron.conway@utoronto.ca
#       institute: [PMCC, LBFON, QUT]
#       correspondence: true
#   - Megan Bittner BSc:
#       institute: [LBFON]
#       correspondence: false
#   - Dan Phan BSc:
#       institute: [LBFON]
#       correspondence: false
#   - Kristina Chang MScN:
#       institute: [PMCC]
#       correspondence: false
#   - Elizabeth Tipton PhD:
#       institute: [NW]
#       correspondence: false
#   - Matteo Parotto MD, PhD:
#       institute: [TGH, UoT]
#       correspondence: false
# institute:
#   - PMCC: Peter Munk Cardiac Centre, University Health Network
#   - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   - QUT: School of Nursing, Queensland University of Technology (QUT)
#   - NW: Department of Statistics, Northwestern University
#   - TGH: Department of Anesthesia and Pain Management, Toronto General Hospital, UHN
#   - UoT: Department of Anesthesia and Interdepartmental Division of Critical Care Medicine, University of Toronto
# output:
#   bookdown::word_document2:
#     reference_docx: Extras/manuscript_template.docx
#     pandoc_args:
#       - --csl=Extras/anesthesiology.csl
#       - --lua-filter=Extras/scholarly-metadata.lua
#       - --lua-filter=Extras/author-info-blocks.lua
params:
  distill: TRUE
  word: FALSE
always_allow_html: true
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(include=FALSE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggprisma) # https://github.com/awconway/ggprisma
library(kableExtra)
library(knitr)
library(magrittr)
source("R/loa_maker.R")
source("R/meta.R")
```

@@

##### Page break

")
```
```{r load-data, include=FALSE}
data <- readxl::read_xlsx(here::here("manuscript", "data", "zhf_extracted.xlsx"))
```

@@

</blockquote>
</div>
```{r conditional_page_break, results='asis', include=params$word}
cat("
##### Page break
")
```
## Introduction

@@

```{r  conditional_references, include=params$word, results='asis'}
cat("##### Page break

@@

```{r  conditional_figure_legend, include=params$word, results='asis'}
cat("##### Page break

>>>>

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
subtitle: A systematic review and meta-analysis
description: "A systematic review and meta-analysis"
# author:
# - name: Aaron Conway
#   affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   email: aaron.conway@utoronto.ca
#   url: https://www.aaronconway.info
# - name: Megan Bittner
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
# - name: Dan Phan
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
# - name: Navpreet Kamboj
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   email: navpreet.kamboj@mail.utoronto.ca
# - name: Kristina Chang
#   affiliation: Toronto General Hospital, UHN
# - name: Elizabeth Tipton
#   affiliation: Department of Statistics, Northwestern University
# - name: Matteo Parotto
#   affiliation: Toronto General Hospital, UHN
# date: "`r Sys.Date()`"
# repository_url: https://github.com/awconway/zhf-review
# twitter:
#   creator: "@aw_conway"
# output: distill::distill_article
bibliography: Extras/bibliography.bib
csl: Extras/anesthesiology.csl
author:
  - Aaron Conway PhD:
      email: aaron.conway@utoronto.ca
      phone: +1 416 946 7112
      address: 585 University Ave, 4NU - 476 | Toronto, ON  M5G 2N2
      institute: [PMCC, LBFON, QUT]
      correspondence: true
  - Megan Bittner BSc:
      institute: [LBFON]
      correspondence: false
  - Dan Phan BSc:
      institute: [LBFON]
      correspondence: false
  - Kristina Chang MScN:
      institute: [PMCC]
      correspondence: false
  - Navpreet Kamboj BScN:
      institute: [LBFON]
      correspondence: false
  - Elizabeth Tipton PhD:
      institute: [NW]
      correspondence: false
  - Matteo Parotto MD, PhD:
      institute: [TGH, UoT]
      correspondence: false
institute:
  - PMCC: Peter Munk Cardiac Centre, University Health Network, Toronto, Canada
  - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto, Toronto, Canada
  - QUT: School of Nursing, Queensland University of Technology (QUT), Brisbane, Australia
  - NW: Department of Statistics, Northwestern University, Evanston, IL, United States
  - TGH: Department of Anesthesia and Pain Management, Toronto General Hospital, UHN, Toronto, Canada
  - UoT: Department of Anesthesia and Interdepartmental Division of Critical Care Medicine, University of Toronto, Toronto, Canada
output:
  bookdown::word_document2:
    reference_docx: Extras/manuscript_template.docx
    pandoc_args:
      - --lua-filter=Extras/scholarly-metadata.lua
      - --lua-filter=Extras/author-info-blocks.lua
      - --lua-filter=Extras/pagebreak.lua
always_allow_html: true
params:
  distill: FALSE
  word: TRUE
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(include=FALSE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggprisma) # https://github.com/awconway/ggprisma
library(kableExtra)
library(knitr)
library(magrittr)
source("R/loa_maker.R")
source("R/meta.R")
```
\pagebreak

@@

")
```

```{r load-data, include=FALSE}
data <- readxl::read_xlsx(here::here("manuscript", "data", "zhf_extracted.xlsx"))
```

@@

</blockquote>
</div>

\pagebreak

## Introduction

@@

\pagebreak

```{r  conditional_references, include=params$word, results='asis'}
cat("

@@

\pagebreak
```{r  conditional_figure_legend, include=params$word, results='asis'}
cat("
